---
title: "marriage_data"
author: "Grace Gao"
date: "3/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
```{r packages}
library("readxl")
library(tidyverse)
library('xml2')
library(rvest)
library(openxlsx)
library(readxl)
library(writexl)
library(dplyr)

```

###read in Excel

```{r read_data}
temp_marriage_data <- read_excel("webscrape_data.xlsx")
```

### turn urls into vector

```{r url_vector}

vector_url_combined <- as.vector(unlist(temp_marriage_data['full_url']))
##create data frame
test_marriage_df <-data.frame()


```
###Loop through url

```{r create_loop}
##loops through the rows -- each url
  i = 1
for(value in vector_url_combined){
  #print(antwerp_engraver_url_data[i, ])
  #antwerp_engraver_link = antwerp_engraver_url_data[i, ]

  print(value)
  #print("count")
  print(i)
  i = i+1
  results_vector_marriage = read_html(value) #read's html of each link page
 
  ##getting child
  marriage_filter <- results_vector_marriage %>% 
  html_nodes("ul li a") %>% 
  html_attr("rel") %>% 
  as_tibble() %>% 
  mutate(id = row_number()) %>% 
  filter(str_detect(value, "spouse"))

  marriage_filter


  marriage_text <- results_vector_marriage  %>% 
    html_nodes("ul li a") %>% 
    html_text() %>% 
    as_tibble() %>% 
    rename(text = value) %>% 
    mutate(id = row_number()) %>% 
    inner_join(marriage_filter)
  
  #marriage_text

  #put the spouse into a vector
  marriage_text_col <- marriage_text %>%
    select(text)

  marriage_vector <- as.vector(t(marriage_text_col))
  
  #df$marriage <- list(marriage_vector)
  
  #extracting count of children
  rownum <- nrow(marriage_text)
  print(rownum)

  marriage_list <- list(marriage_vector)
  string_spouse <- paste(marriage_list, collapse=', ' )
  
  rownum_tibble <- tibble(value, rownum, string_spouse)
  #num_children_df = bind_rows(num_children_df, rownum_tibble)
  test_marriage_df = bind_rows(test_marriage_df, rownum_tibble)

Sys.sleep(2)

}

```


#code to convert list into string
list_vector <- list(marriage_vector)
list_vector
unlist_vector <- unlist(list_vector)
unlist_vector

string_spouse <- paste(list_vector, collapse=', ' )
string_spouse



###First test

```{r firsthalf}
glimpse(test_marriage_df)
```
```{r}

write_xlsx(x = test_marriage_df, path = "test_marriage_data.xlsx", col_names = TRUE)

```


### Marriage Example Webscrape
```{r}
emanuel <-  read_html("http://www.vondel.humanities.uva.nl/ecartico/persons/3160")



marriage_filter <- emanuel %>% 
  html_nodes("ul li a") %>% 
  html_attr("rel") %>% 
  as_tibble() %>% 
  mutate(id = row_number()) %>% 
  filter(str_detect(value, "spouse"))
marriage_filter

marriage_text <- emanuel  %>% 
  html_nodes("ul li a") %>% 
  html_text() %>% 
  as_tibble() %>% 
  rename(text = value) %>% 
  mutate(id = row_number()) %>% 
  inner_join(marriage_filter)

marriage_text %>%
  pull(text)
```

```{r}

##turning the stuff into columns

marriage_text

marriage_text_col <- marriage_text %>%
  select(text)

marriage_vector <- as.vector(t(marriage_text_col))
marriage_vector

df$marriage <- list(marriage_vector)

glimpse(df)

```