---
title: "antwerp_initial"
author: "Grace Gao"
date: "12/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load library packages

```{r}
library(tidyverse)
library(rvest)
library(xlsx)
library(writexl)
```

##Scrapping the URLs
Scrap all the URLs for every artist in the whole Database

#### Import a webpage using `read_html`

```{r get_pageoneurl}
results_antwerp <- read_html("http://www.vondel.humanities.uva.nl/ecartico/persons/index.php?occupation_id=56%2C79%2C542&subjectmat=&place=Antwerpen&gender=&year_start=1556&year_end=1725&formtype=selections&page=1&subtask=selections")
```

```{r display_htmlpage}
#displaying the html page
#results_antwerp
```

### Getting text of first page
Quick Info:
li = list node in HTML
html_text: Extract attributes, text and tag name from HTML.

```{r extract_pageone_text}
names_antwerp <- results_antwerp %>% 
  html_nodes("li") %>% 
  html_text()

names_antwerp
```

### Parsing to get the individual links
href: <a href="https://www.w3schools.com">Visit W3Schools.com!</a>
href allows you to click on the artist name and be redirected to their page

```{r text_url_pageone}
url_antwerp <- results_antwerp %>% 
  html_nodes("li a") %>% 
  html_attr("href")

url_antwerp #list of individual links from page one
```

### Create a tibble

Puts the vectors of names and url into a tibble to be easily accesible

```{r tibble_pageone}
results_df_antwerp <- tibble(names_antwerp, url_antwerp)

results_df_antwerp
```

This section we mutate the urls in the dataset to represent the actual urls (utilizing glue and mutate)

```{r mutate_url}
#url
results_df_antwerp <- results_df_antwerp %>% 
  mutate(base_url = "http://www.vondel.humanities.uva.nl") %>% 
  mutate(full_url = glue::glue("{base_url}{url_antwerp}")) %>% 
  mutate(full_url = str_replace_all(full_url, "\\.\\.", ""))

results_df_antwerp
```


#### Import a webpage using `read_html` Antwerp pg 2

```{r get_pageoneurl}
results_antwerp_2 <- read_html("http://www.vondel.humanities.uva.nl/ecartico/persons/index.php?occupation_id=56%2C79%2C542&subjectmat=&place=Antwerpen&gender=&year_start=1556&year_end=1725&formtype=selections&page=2&subtask=selections")
```

```{r display_htmlpage}
#displaying the html page
#results_antwerp_2
```

### Getting text of first page
Quick Info:
li = list node in HTML
html_text: Extract attributes, text and tag name from HTML.

```{r extract_pageone_text}
names_antwerp <- results_antwerp_2 %>% 
  html_nodes("li") %>% 
  html_text()

names_antwerp
```

### Parsing to get the individual links
href: <a href="https://www.w3schools.com">Visit W3Schools.com!</a>
href allows you to click on the artist name and be redirected to their page

```{r text_url_pageone}
url_antwerp<- results_antwerp_2 %>% 
  html_nodes("li a") %>% 
  html_attr("href")

url_antwerp #list of individual links from page one
```

### Create a tibble

Puts the vectors of names and url into a tibble to be easily accesible

```{r tibble_pageone}
results_df_antwerp_2 <- tibble(names_antwerp, url_antwerp)

results_df_antwerp_2
```

```{r mutate_url}
#url
results_df_antwerp_2 <- results_df_antwerp_2 %>% 
  mutate(base_url = "http://www.vondel.humanities.uva.nl") %>% 
  mutate(full_url = glue::glue("{base_url}{url_antwerp}")) %>% 
  mutate(full_url = str_replace_all(full_url, "\\.\\.", ""))


results_df_antwerp_2
```
```{r tibble_new}

df_antwerp_smith <- bind_rows(results_df_antwerp, results_df_antwerp_2)

```


```{r tibble_pageone}
write_xlsx(x = df_antwerp_smith, path = "antwerp_smith_data.xlsx", col_names = TRUE)
```
