---
title: "antwerp_printers_data"
author: "Grace Gao"
date: "12/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load library packages

```{r}
library(tidyverse)
library(rvest)
library(xlsx)
library(writexl)
```

##Scrapping the URLs
Scrap all the URLs for every artist in the whole Database

###Webscraping for the URLs of Printers, booksellers and publishers: Male
#### Import a webpage using `read_html`

```{r get_pageoneurl}
results_antwerp_book <- read_html("http://www.vondel.humanities.uva.nl/ecartico/persons/index.php?occupation_id=28%2C663%2C29%2C658%2C32%2C30%2C1028%2C243&subjectmat=&place=antwerpen&gender=male&year_start=1556&year_end=1725&formtype=selections&page=1&subtask=selections")
```

### Getting text of first page
Quick Info:
li = list node in HTML
html_text: Extract attributes, text and tag name from HTML.

```{r extract_pageone_text}
names_antwerp_book <- results_antwerp_book %>% 
  html_nodes("li") %>% 
  html_text()

names_antwerp_book
```

### Parsing to get the individual links
href: <a href="https://www.w3schools.com">Visit W3Schools.com!</a>
href allows you to click on the artist name and be redirected to their page

```{r text_url_pageone}
url_antwerp_book <- results_antwerp_book %>% 
  html_nodes("li a") %>% 
  html_attr("href")

url_antwerp_book #list of individual links from page one
```

### Create a tibble

Puts the vectors of names and url into a tibble to be easily accesible

```{r tibble_pageone}
results_df_antwerp_book <- tibble(names_antwerp_book, url_antwerp_book)

results_df_antwerp_book
```

This section we mutate the urls in the dataset to represent the actual urls (utilizing glue and mutate)

```{r mutate_url}
results_df_antwerp_book <- results_df_antwerp_book %>% 
  mutate(base_url = "http://www.vondel.humanities.uva.nl") %>% 
  mutate(full_url = glue::glue("{base_url}{url_antwerp_book}")) %>% 
  mutate(full_url = str_replace_all(full_url, "\\.\\.", ""))

results_df_antwerp_book
```


#### Import a webpage using `read_html` Antwerp - Printers, booksellers and publishers: Male - pg 2

```{r get_pagetwobookurl}
results_antwerp_book2 <- read_html("http://www.vondel.humanities.uva.nl/ecartico/persons/index.php?occupation_id=28%2C663%2C29%2C658%2C32%2C30%2C1028%2C243&subjectmat=&place=antwerpen&gender=male&year_start=1556&year_end=1725&formtype=selections&page=2&subtask=selections")
```
### Getting text of second page
```{r extract_book2}
names_antwerp_book <- results_antwerp_book2 %>% 
  html_nodes("li") %>% 
  html_text()

#names_antwerp_book
```
### Parsing to get the individual links
```{r text_url_pageone}
url_antwerp_book <- results_antwerp_book2 %>% 
  html_nodes("li a") %>% 
  html_attr("href")

url_antwerp_book #list of individual links from page one
```
### Create a tibble
```{r tibble_pageone}
results_df_antwerp_book2 <- tibble(names_antwerp_book, url_antwerp_book)

#results_df_antwerp_book2

```
###Mutating to create new url
```{r mutate_url}
results_df_antwerp_book2 <- results_df_antwerp_book2 %>% 
  mutate(base_url = "http://www.vondel.humanities.uva.nl") %>% 
  mutate(full_url = glue::glue("{base_url}{url_antwerp_book}")) %>% 
  mutate(full_url = str_replace_all(full_url, "\\.\\.", ""))

#results_df_antwerp_book2
```

### Converting tibbles into Excel Files
```{r tibble_new}

df_antwerp_book <- bind_rows(results_df_antwerp_book, results_df_antwerp_book2)

```

```{r create_excel}
write_xlsx(x = df_antwerp_book, path = "antwerp_book_data.xlsx", col_names = TRUE)
```

#### Import a webpage using `read_html` Antwerp - Printers, booksellers and publishers: Female

```{r get_pagetwobookurl}
results_antwerp_book_fem <- read_html("http://www.vondel.humanities.uva.nl/ecartico/persons/index.php?occupation_id=28%2C663%2C29%2C658%2C32%2C30%2C1028%2C243&subjectmat=&place=antwerpen&gender=female&year_start=1556&year_end=1725&formtype=selections&page=1&subtask=selections")
```
### Getting text of second page
```{r extract_book2}
names_antwerp_book_fem <- results_antwerp_book_fem %>% 
  html_nodes("li") %>% 
  html_text()

names_antwerp_book_fem
```
### Parsing to get the individual links
```{r text_url_pageone}
url_antwerp_book_fem <- results_antwerp_book_fem %>% 
  html_nodes("li a") %>% 
  html_attr("href")

url_antwerp_book_fem #list of individual links from page one
```
### Create a tibble
```{r tibble_pageone}
results_df_antwerp_book_fem <- tibble(names_antwerp_book_fem, url_antwerp_book_fem)

#results_df_antwerp_book2

```
###Mutating to create new url
```{r mutate_url}
results_df_antwerp_book_fem <- results_df_antwerp_book_fem %>% 
  mutate(base_url = "http://www.vondel.humanities.uva.nl") %>% 
  mutate(full_url = glue::glue("{base_url}{url_antwerp_book_fem}")) %>% 
  mutate(full_url = str_replace_all(full_url, "\\.\\.", ""))

results_df_antwerp_book_fem
```

### Converting tibbles into Excel Files

```{r create_excel}
#write_xlsx(x = results_df_antwerp_book_fem, path = "antwerp_book_fem_data.xlsx", col_names = TRUE)
```